Studying the Performance of the Jellyfish Optimiser for the Application of Projection Pursuit

### 2024-05-31 optim.qmd
write up on exmaple #2

## Smoothness

@@

## Squintability

@@

## On skewness and kurtosis index

@@

construct a relationship between jellyfish success and jellyfish
parameters and the optimisation properties defined in @sec-theory.

This can imform the choice of jellyfish parameters for a given
optimisation problem.

In addition to the pipe-finding problem, we also consider the problem of
finding the sine wave structure in the 6D space and six indexes
(`dcor2d_2`, `loess2d`, `MIC`, `TIC`, `spline`, and `stringy`) are
considered. Combined with the jellyfish optimisers (`n_jellies` =
20/50/100, `max_tries` = 50/100), we obtain additional 27 setups for
this investigation.

```{r}
load(here::here("data/smoothness.rda"))
smoothness |> knitr::kable(digits = 3)
load(here::here("data/squintability.rda"))
squintability |> knitr::kable(digits = 3)
```

```{r}
#| fig.width = 8,
#| fig.height = 5,
#| fig.cap = "sdkflskdfjl"
load(here::here("data/sq_basis_dist_idx.rda"))
sq_basis_dist_idx |>
  ggplot(aes(x = dist, y = idx, group = index)) +
  geom_line() +
  facet_nested_wrap(~index + n, nrow = 3, labeller = label_both, scales = "free_y") + 
  xlab("projection distance") + ylab("index value")

@@

>>>>

## Smoothness {#sec-smoothness}

@@

## Squintability {#sec-squintability}

@@

\newpage

@@

[TODO: overall summary]construct a relationship between jellyfish success and jellyfish parameters and the optimisation properties defined in @sec-theory. This can inform the choice of jellyfish parameters for a given
optimisation problem.

In addition to the pipe-finding problem, the sine-wave finding problem is also investigated in 6D and 8D spaces. Six indices are considered: `dcor2d_2`, `loess2d`, `MIC`, `TIC`, `spline`, and `stringy`, which gives the 12 problems printed as rows in @tbl-smoothness-squintability. Combining these problems with different jellyfish optimiser parameters (`n_jellies` and `max_tries`), a total of 51 observations is produced, comprising of 24 observations for the pipe-finding and 27 observations for the sine-wave finding.

For each observation, fifty (50) runs of the jellyfish optimisation is performed. In each run, summary statistics are calculated to find the best index across all the jellyfishes (`I_max`) and the proportion of jellyfishes found (`P_J`). At the observation level, the best index value across all the 50 runs  (`I_max_max`) and the proportion of trials found (`P_J_hat`) is calculated.

Smoothness and squintability measures are computed for each problem, following the procedures outlined in @sec-smoothness and @sec-squintability. To calculate smoothness, 300 random bases are used to estimate Gaussian process parameters (variance, range, smoothness, and nugget). For squintability, 50 random bases are sampled and interpolated to the optimal basis using a step size of 0.005. The index value and projection distance are calculated for all the interpolated bases. A binning procedure is then applied to average the index value at each bin width of 0.005. Finally, the scaled logistic function with four parameters (theta1 - theta4) is estimated by non-linear least square to obtain the squintability measure.

@tbl-smoothness-squintability presents all the parameters calculated for smoothness and squintability, with the column "smooth" for smoothness and "theta3" for squintability. @fig-idx-proj-dist shows the relationship between the index value against the projection distance for each problem following the binning procedure. @tbl-all-sim displays the first five rows after combining all calculations.

```{r}
#| label: tbl-smoothness-squintability
#| tbl-cap: Parameters estimated from the Gaussian process (including variance, range, smoothness, and nugget) and scaled logistic function (theta1 - theta4) for both the pipe-finding and sine-wave finding problems. The "smooth" and "theta3" column represent the smoothness and squintability measures. 
load(here::here("data/smoothness.rda"))
load(here::here("data/squintability.rda"))
library(kableExtra)
tibble(shape = c(rep("pipe", 4), rep("sine", 8)), smoothness) |>
  left_join(squintability) |> 
  rename(d = n, smooth = smoothness) |> 
  knitr::kable(digits = 3) |> 
  column_spec(1, border_left = TRUE) |> 
  column_spec(c(3, 7, 11), border_right = TRUE) |> 
  kable_styling(latex_options = "hold_position")
```

```{r fig-idx-proj-dist}
#| fig.width = 9,
#| fig.height = 5,
#| fig.cap = "Index values against projection distance for the 12 pipe/sine-wave finding problem after the binning procedure during the estimation of the squintability measure. The index value is averaged at each bin width of 0.005 and the TIC index is scaled to 0-1 for comparison. When finding the sine-wave structure using the MIC and TIC index, a convex curved is observed, as opposed to the pipe-finding problem or the sine-wave finding problem with the dcor2d\\_2, loess2d, and splines2d index. When finding the sine-wave with the stringy index, the index shows an instantaneous jump to the optimum when close to the best basis."
load(here::here("data/sq_basis_dist_idx.rda"))
sq_basis_dist_idx |>
  ggplot(aes(x = dist, y = idx, group = index)) +
  geom_line() +
  facet_nested_wrap(~index + n, nrow = 3, labeller = label_both, scales = "free_y") + 
  xlab("projection distance") + ylab("index value")

@@

```{r}
#| label: tbl-all-sim
#| tbl-cap: The first five rows of the datasets after combining all the calculation. The smoothness and squintability variable are uniquely characterised by the index function used and the data dimension, and thus do not vary across n\\_jellies and max\\_tries. Variables I\\_max\\_max, P\\_J\\_hat, and time are calculated at each 51 observations.
load(here::here("data/sim_df.rda"))
sim_df |> 
  dplyr::select(index, d, smoothness, squintability, n_jellies, max_tries, 
                I_max_max, P_J_hat, time) |> 
  arrange(index, d, n_jellies, max_tries) |> 
  head(5) |> 
  kable(digits = 3)
```

### 2024-05-31 optim.tex
write up on exmaple #2

\usepackage{algorithm}
\usepackage{algpseudocode}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal of Multivariate Analysis}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}
\usepackage{bookmark}

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, coltitle=black, toptitle=1mm, toprule=.15mm, leftrule=.75mm, left=2mm, colback=white, opacitybacktitle=0.6, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomtitle=1mm, rightrule=.15mm]

@@

\subsection{Smoothness}\label{smoothness}

@@

\subsection{Squintability}\label{squintability}

@@

\subsection{On skewness and kurtosis
index}\label{on-skewness-and-kurtosis-index}

@@

construct a relationship between jellyfish success and jellyfish
parameters and the optimisation properties defined in
Section~\ref{sec-theory}.

This can imform the choice of jellyfish parameters for a given
optimisation problem.

In addition to the pipe-finding problem, we also consider the problem of
finding the sine wave structure in the 6D space and six indexes
(\texttt{dcor2d\_2}, \texttt{loess2d}, \texttt{MIC}, \texttt{TIC},
\texttt{spline}, and \texttt{stringy}) are considered. Combined with the
jellyfish optimisers (\texttt{n\_jellies} = 20/50/100,
\texttt{max\_tries} = 50/100), we obtain additional 27 setups for this
investigation.

\begin{longtable}[]{@{}lrrrrr@{}}
\toprule\noalign{}
index & n & variance & range & smoothness & nugget \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
holes & 6 & 0.002 & 0.408 & 2.364 & 0.212 \\
holes & 8 & 0.000 & 0.259 & 2.373 & 0.613 \\
holes & 10 & 0.000 & 0.144 & 2.317 & 1.831 \\
holes & 12 & 0.000 & 0.254 & 2.173 & 0.879 \\
MIC & 6 & 0.016 & 0.100 & 2.394 & 0.087 \\
MIC & 8 & 0.016 & 0.100 & 2.394 & 0.087 \\
TIC & 6 & 0.124 & 0.104 & 2.471 & 0.086 \\
TIC & 8 & 0.124 & 0.104 & 2.471 & 0.086 \\
dcor2d\_2 & 6 & 0.034 & 0.167 & 2.663 & 0.114 \\
loess2d & 6 & 0.083 & 0.307 & 2.194 & 0.292 \\
splines2d & 6 & 0.040 & 0.189 & 2.606 & 0.104 \\
stringy & 6 & 0.000 & 1173.035 & 1.031 & 17608.047 \\
\end{longtable}

\begin{longtable}[]{@{}lrrrrr@{}}
\toprule\noalign{}
index & n & theta1 & theta2 & theta3 & theta4 \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
holes & 6 & 1.001 & 0.860 & 3.368 & 0.823 \\
holes & 8 & 1.001 & 0.869 & 3.264 & 0.811 \\
holes & 10 & 1.000 & 0.885 & 3.151 & 0.806 \\
holes & 12 & 1.000 & 0.878 & 3.345 & 0.806 \\
MIC & 6 & 0.894 & 0.571 & 1.623 & -0.024 \\
MIC & 8 & 0.932 & 0.328 & 1.314 & -0.030 \\
TIC & 6 & 0.951 & 0.536 & 1.719 & -0.025 \\
TIC & 8 & 0.945 & 0.564 & 1.723 & -0.027 \\
dcor2d\_2 & 6 & 0.954 & 1.039 & 2.742 & -0.019 \\
loess2d & 6 & 1.016 & 1.039 & 2.648 & 0.080 \\
splines2d & 6 & 1.014 & 1.051 & 2.730 & -0.009 \\
stringy & 6 & 1.011 & 0.011 & 254.734 & 0.727 \\
\end{longtable}

{\centering \includegraphics{optim_files/figure-pdf/unnamed-chunk-10-1.pdf}

@@

\caption{sdkflskdfjl}

@@

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal of Multivariate Analysis}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}
\usepackage{bookmark}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, arc=.35mm, leftrule=.75mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, colbacktitle=quarto-callout-note-color!10!white, bottomtitle=1mm, toptitle=1mm, opacityback=0, bottomrule=.15mm, titlerule=0mm, coltitle=black, rightrule=.15mm, breakable, toprule=.15mm, left=2mm]

@@

\subsection{Smoothness}\label{sec-smoothness}

@@

\subsection{Squintability}\label{sec-squintability}

@@

\newpage

@@

{[}TODO: overall summary{]}construct a relationship between jellyfish
success and jellyfish parameters and the optimisation properties defined
in Section~\ref{sec-theory}. This can inform the choice of jellyfish
parameters for a given optimisation problem.

In addition to the pipe-finding problem, the sine-wave finding problem
is also investigated in 6D and 8D spaces. Six indices are considered:
\texttt{dcor2d\_2}, \texttt{loess2d}, \texttt{MIC}, \texttt{TIC},
\texttt{spline}, and \texttt{stringy}, which gives the 12 problems
printed as rows in Table~\ref{tbl-smoothness-squintability}. Combining
these problems with different jellyfish optimiser parameters
(\texttt{n\_jellies} and \texttt{max\_tries}), a total of 51
observations is produced, comprising of 24 observations for the
pipe-finding and 27 observations for the sine-wave finding.

For each observation, fifty (50) runs of the jellyfish optimisation is
performed. In each run, summary statistics are calculated to find the
best index across all the jellyfishes (\texttt{I\_max}) and the
proportion of jellyfishes found (\texttt{P\_J}). At the observation
level, the best index value across all the 50 runs
(\texttt{I\_max\_max}) and the proportion of trials found
(\texttt{P\_J\_hat}) is calculated.

Smoothness and squintability measures are computed for each problem,
following the procedures outlined in Section~\ref{sec-smoothness} and
Section~\ref{sec-squintability}. To calculate smoothness, 300 random
bases are used to estimate Gaussian process parameters (variance, range,
smoothness, and nugget). For squintability, 50 random bases are sampled
and interpolated to the optimal basis using a step size of 0.005. The
index value and projection distance are calculated for all the
interpolated bases. A binning procedure is then applied to average the
index value at each bin width of 0.005. Finally, the scaled logistic
function with four parameters (theta1 - theta4) is estimated by
non-linear least square to obtain the squintability measure.

Table~\ref{tbl-smoothness-squintability} presents all the parameters
calculated for smoothness and squintability, with the column ``smooth''
for smoothness and ``theta3'' for squintability.
Figure~\ref{fig-idx-proj-dist} shows the relationship between the index
value against the projection distance for each problem following the
binning procedure. Table~\ref{tbl-all-sim} displays the first five rows
after combining all calculations.

\begin{longtable}[t]{|>{}ll>{}r|rrr>{}r|rrr>{}r|}

\caption{\label{tbl-smoothness-squintability}Parameters estimated from
the Gaussian process (including variance, range, smoothness, and nugget)
and scaled logistic function (theta1 - theta4) for both the pipe-finding
and sine-wave finding problems. The ``smooth'' and ``theta3'' column
represent the smoothness and squintability measures.}

\tabularnewline

\toprule
shape & index & d & variance & range & smooth & nugget & theta1 & theta2 & theta3 & theta4\\
\midrule
pipe & holes & 6 & 0.002 & 0.408 & 2.364 & 0.212 & 1.001 & 0.860 & 3.368 & 0.823\\
pipe & holes & 8 & 0.000 & 0.259 & 2.373 & 0.613 & 1.001 & 0.869 & 3.264 & 0.811\\
pipe & holes & 10 & 0.000 & 0.144 & 2.317 & 1.831 & 1.000 & 0.885 & 3.151 & 0.806\\
pipe & holes & 12 & 0.000 & 0.254 & 2.173 & 0.879 & 1.000 & 0.878 & 3.345 & 0.806\\
sine & MIC & 6 & 0.016 & 0.100 & 2.394 & 0.087 & 0.894 & 0.571 & 1.623 & -0.024\\
\addlinespace
sine & MIC & 8 & 0.016 & 0.100 & 2.394 & 0.087 & 0.932 & 0.328 & 1.314 & -0.030\\
sine & TIC & 6 & 0.124 & 0.104 & 2.471 & 0.086 & 0.951 & 0.536 & 1.719 & -0.025\\
sine & TIC & 8 & 0.124 & 0.104 & 2.471 & 0.086 & 0.945 & 0.564 & 1.723 & -0.027\\
sine & dcor2d\_2 & 6 & 0.034 & 0.167 & 2.663 & 0.114 & 0.954 & 1.039 & 2.742 & -0.019\\
sine & loess2d & 6 & 0.083 & 0.307 & 2.194 & 0.292 & 1.016 & 1.039 & 2.648 & 0.080\\
\addlinespace
sine & splines2d & 6 & 0.040 & 0.189 & 2.606 & 0.104 & 1.014 & 1.051 & 2.730 & -0.009\\
sine & stringy & 6 & 0.000 & 1173.035 & 1.031 & 17608.047 & 1.011 & 0.011 & 254.734 & 0.727\\
\bottomrule

\end{longtable}

\begin{figure}

\centering{

\includegraphics{optim_files/figure-pdf/fig-idx-proj-dist-1.pdf}

@@

\caption{\label{fig-idx-proj-dist}Index values against projection
distance for the 12 pipe/sine-wave finding problem after the binning
procedure during the estimation of the squintability measure. The index
value is averaged at each bin width of 0.005 and the TIC index is scaled
to 0-1 for comparison. When finding the sine-wave structure using the
MIC and TIC index, a convex curved is observed, as opposed to the
pipe-finding problem or the sine-wave finding problem with the
dcor2d\_2, loess2d, and splines2d index. When finding the sine-wave with
the stringy index, the index shows an instantaneous jump to the optimum
when close to the best basis.}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0714}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0357}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1310}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1667}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1190}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1190}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1190}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0952}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1429}}@{}}

\caption{\label{tbl-all-sim}The first five rows of the datasets after
combining all the calculation. The smoothness and squintability variable
are uniquely characterised by the index function used and the data
dimension, and thus do not vary across n\_jellies and max\_tries.
Variables I\_max\_max, P\_J\_hat, and time are calculated at each 51
observations.}

\tabularnewline

\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
index
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
d
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
smoothness
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
squintability
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
n\_jellies
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
max\_tries
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
I\_max\_max
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
P\_J\_hat
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
time
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
MIC & 6 & 2.394 & 1.623 & 20 & 50 & 0.999 & 1.00 & 2.479 secs \\
MIC & 6 & 2.394 & 1.623 & 20 & 100 & 0.999 & 0.96 & 8.950 secs \\
MIC & 6 & 2.394 & 1.623 & 50 & 50 & 1.000 & 1.00 & 5.651 secs \\
MIC & 6 & 2.394 & 1.623 & 50 & 100 & 1.000 & 0.64 & 13.223 secs \\
MIC & 6 & 2.394 & 1.623 & 100 & 50 & 1.000 & 0.76 & 19.453 secs \\

\end{longtable}
